A Parallel Geometric Multigrid Algorithm

### 2013-12-12 trunk/htdocs/electrokinetic.tex
Added PETSc scaling
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2278 40876441-3496-0410-a613-a2fca35b2ae2

Taking the gradient of the stress tensor gives

@@

\begin{figure}[htpb]
\includegraphics[width=0.9\textwidth]{./pics/scaling.pdf}
\caption{Scaling of a system of $128^3$ lattice sites on up to 512 MPI tasks. 
While the scaling for the Nernst Planck part of the calulcation are reasonable, 
it can be seen that the SOR routine used to solve the Poisson equation deviates
strongly from ideal behaviour.} 
\label{fig5} 
\end{figure}
\clearpage

>>>>

Taking the divergence of the stress tensor gives

@@

\begin{figure}[htpb]
\includegraphics[width=0.9\textwidth]{./pics/scaling.pdf}
\caption{Scaling of a system of $128^3$ lattice sites on up to 512 MPI tasks. 
While the scaling for the Nernst Planck part of the calulcation are reasonable, 
it can be seen that the SOR routine used to solve the Poisson equation deviates
strongly from ideal behaviour.} 
\label{fig5} 
\end{figure}

\subsubsection{Scaling with Krylov Subspace Solver}

We use a Krylov subspace solver from the Portable Extendabl Toolkit for Scientific Computation (PETSc.

\begin{figure}[htpb]
\includegraphics[width=0.9\textwidth]{./pics/petsc_scaling.pdf}
\caption{Scaling of a system of $128^3$ lattice sites on up to 4096 MPI tasks. 
The scaling of both the Nernst Planck part as well as the Poisson solver are only limited by the overhead of communication to computation at very small decompositions.} 
\label{fig6} 
\end{figure}
\clearpage
